---
title: "R Group Assignment COVID"
author: "Jenefa, Oxana, Yiqi, Raph, Hongdi"
date: "7/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

</style>

<h3 class = 'menutop' id="Contents">
  [Contents](#Contents)
  [Introduction](#Introduction)

<div class="dropdown">
<a class="dropbtn">Data analysis</a>
<div class="dropdown-content">
  [dates](#dates)
  [station_location](#station_location)
  [heatmaps](#heatmaps)
</div>
</div>
  [Data Preparation](#data_preparation)
  [Data Processing](#data_processing)
  [Building the Model](#building_the_model)
</h3>
<body style = "font-family: Arial, Helvetica, sans-serif;">
<a center class="anchor" id="Introduction" style="background-color:Gainsboro; width:40%;"></a>
<center style="background-color:Gainsboro; width:40%;">Introduction</center>


> 'We are glad to present to you our R advanced Group Assignment!'

```{r, echo=F}
# Before starting, we have to install and activate some R libraries in order to use the necessary statistics and time series functions:
# basic statistics 
install.packages("fBasics")
# time series functions
install.packages("forecast")
# normality tests
install.packages("normtest")

# working with the excel tables
install.packages("xlsx")
install.packages("readxl")

library(fBasics)
library(forecast)
library(normtest)
library(tidyverse)
library(readxl)
#library(xlsx)


#clean environment
#rm(list=ls())
#File paths:
#Kiko file path
#data<-read.csv("C:/Users/usuario/Desktop/LPC/MASTERS/MBD_abril_2019/Sessions2&3sim.csv",header=TRUE,sep=";",dec=",")

#Oxana file paths
file_path_original_data <- file.path("~","Downloads","Timeseries","Homework_1_DATA .csv")
data<-read.csv(file_path_original_data, header=TRUE,sep=";",dec=",")
summary_table_ts_file <- file.path("~","Downloads","Timeseries","resultsfts.xlsx")
summary_table_ts <- read_excel(summary_table_ts_file, sheet = 1)
tests_table <- read_excel(summary_table_ts_file, sheet = 2)
#summary_table_ts <- read.xlsx(summary_table_ts_file, 1)
#tests_table <-read.xlsx(summary_table_ts_file, 2)

# Data itself
series1=data[,1] [1:300]
series2=data[,2] [1:300]
series3=data[,3] [1:300]
series4=data[,4] [1:300]
series5=data[,5] [1:2000]
series6=data[,6] 
series7=data[,7]
```

<div id= 'summary'>
# Summary of findings 

> 'We decided to also list the tests we used together with the original and transformed data'

```{r date_variant, echo=FALSE}
print(summary_table_ts)
```